\documentclass[11pt,a4paper]{article}

\usepackage[left=0.6in,right=0.6in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}

\titleformat{\section}
{\large\bfseries}
{}{0em}{}[\titlerule]

\setlist[itemize]{noitemsep, topsep=2pt}

\begin{document}

\begin{center}
{\LARGE \textbf{Angadveer Singh}}\\
Ottawa, ON \\
+1 (613) 295-5094 \quad | \quad sidhuangad088@gmail.com \\
\href{https://www.linkedin.com/in/angadveer-singh-46a57916a}{LinkedIn Profile}
\end{center}

\vspace{-0.3cm}

\section*{Professional Summary}

Network Security and Cybersecurity Analyst with experience supporting enterprise network infrastructure, security operations, vulnerability management, firewall technologies, VPN solutions, and infrastructure risk management. Skilled in network monitoring, incident investigation, disaster recovery testing, failover validation, security assessments, and automation using PowerShell and Python. Strong understanding of routing and switching concepts, network security controls, Active Directory environments, and security frameworks including NIST CSF and ISO 27001. Proven ability to collaborate across infrastructure, security, and operations teams to improve reliability, security posture, and operational efficiency.

\section*{Technical Skills}

\textbf{Networking:}
TCP/IP, OSI Model, LAN/WAN, VLANs, Routing, Switching, OSPF, BGP, QoS, VPN, DNS, DHCP, Network Segmentation

\textbf{Network Security:}
Firewall Administration, Security Policies, NAT, Access Control, Threat Prevention, URL Filtering, VPN Technologies, Security Hardening

\textbf{Firewall Technologies:}
Palo Alto NGFW, Cisco ASA, Fortinet FortiGate, Check Point Firewall Concepts

\textbf{Routing \& Switching:}
Cisco Routing and Switching, Cisco Nexus, Cisco Meraki, Inter-VLAN Routing, Layer 2 and Layer 3 Networking

\textbf{Security Operations:}
Incident Response, Vulnerability Management, Risk Assessment, Security Monitoring, Root Cause Analysis, Threat Mitigation

\textbf{Monitoring \& Management Tools:}
SolarWinds, Azure Sentinel, Datadog, Kiwi Syslog, CiscoWorks, HP OpenView, SCCM, ServiceNow, JIRA

\textbf{Operating Systems \& Infrastructure:}
Windows Server 2016/2019, Windows 10/11, Active Directory, O365, Linux, VMware ESXi, vCenter

\textbf{Automation \& Scripting:}
PowerShell, Python, Bash, Ansible Basic

\textbf{Cloud \& Virtualization:}
Microsoft Azure, Azure VNets, NSGs, VPN Gateway, ExpressRoute, AWS VPC, VMware

\textbf{Frameworks \& Methodologies:}
ITIL v4, Agile, SCRUM, Change Management, Problem Management, NIST Cybersecurity Framework, ISO 27001, CIS Controls, MITRE ATT\&CK

\textbf{Operational Areas:}
Network Monitoring, Incident Investigation, Vulnerability Remediation, Disaster Recovery Testing, Failover Validation, Infrastructure Risk Assessment, Production Deployment Support

\section*{Professional Experience}

\textbf{Network Security Analyst} \hfill Jul 2022 -- Aug 2023\\
\textit{KPMG Assurance and Consulting Services LLP, India}

\begin{itemize}[leftmargin=*]
\item Supported enterprise network security operations across multi-site environments, including firewall administration, VPN technologies, access-control mechanisms, and network security monitoring.

\item Assisted with network security enhancements, firewall policy reviews, routing validation, NAT review, and infrastructure security assessments across enterprise environments.

\item Monitored security events, analyzed logs, investigated network-related incidents, and collaborated with infrastructure teams to identify root causes and implement corrective actions.

\item Participated in vulnerability assessment and remediation activities by reviewing security findings, validating security controls, and tracking corrective actions based on risk and business impact.

\item Supported Palo Alto firewall administration activities, including security policy reviews, access-rule validation, traffic analysis, and change implementation support.

\item Assisted with VPN connectivity troubleshooting, remote-access issues, proxy policy reviews, and secure access solutions supporting distributed enterprise users.

\item Supported disaster recovery exercises, failover validation, business continuity activities, and infrastructure risk assessments to strengthen operational resilience.

\item Developed PowerShell automation scripts for log analysis, configuration auditing, and operational reporting, reducing manual effort and improving troubleshooting efficiency.

\item Supported Active Directory access governance activities including privileged access reviews, user access validation, and access-control compliance checks.

\item Collaborated with network, security, and infrastructure teams to support upgrades, production changes, security enhancements, and continuous improvement initiatives.

\item Maintained network diagrams, firewall documentation, operational procedures, incident records, remediation trackers, and change-management records aligned with ITIL practices.
\end{itemize}

\textbf{NOC Analyst Intern} \hfill Jan 2022 -- Jul 2022\\
\textit{KPMG Assurance and Consulting Services LLP, India}

\begin{itemize}[leftmargin=*]
\item Monitored enterprise network infrastructure, security events, system availability, and performance alerts using SolarWinds and centralized logging platforms.

\item Assisted with troubleshooting routing, switching, firewall, VPN, and connectivity issues across enterprise environments.

\item Investigated network outages, performance degradation, service interruptions, and policy violations using structured troubleshooting methodologies.

\item Supported firewall policy implementation, VPN configuration activities, proxy policy changes, and network security change requests under supervision.

\item Participated in incident management, change management, and problem management processes following ITIL best practices.

\item Reviewed network monitoring alerts, escalated critical issues, and coordinated with infrastructure and security teams for timely resolution.

\item Created network topology diagrams, operational documentation, post-change reviews, and post-incident reports using Microsoft Visio.

\item Assisted with vulnerability remediation activities and validation of security control implementations.
\end{itemize}

\section*{Projects}

\textbf{Automated Cloud Security Incident Response Framework -- Azure Sentinel}

\begin{itemize}[leftmargin=*]
\item Designed and implemented an automated security incident response workflow using Azure Sentinel, Logic Apps, and Python scripting.

\item Automated triage and enrichment of authentication anomalies, privilege escalation alerts, and suspicious cloud activities.

\item Applied MITRE ATT\&CK mapping, threat-hunting methods, and CIS Benchmark concepts to improve detection and response effectiveness.

\item Developed automation workflows to reduce analyst investigation effort and improve incident response consistency.
\end{itemize}

\textbf{Software-Defined Network Load Balancer -- Python, RYU Controller}

\begin{itemize}[leftmargin=*]
\item Developed an SDN-based load balancing solution using Python, RYU Controller, and OpenFlow.

\item Monitored OpenFlow switch statistics and implemented dynamic traffic-routing logic to optimize throughput and reduce congestion.

\item Applied routing and traffic engineering concepts to improve network utilization and support high-availability service delivery.
\end{itemize}

\section*{Education}

\textbf{Master of Information Systems Security} \hfill Sept 2023 -- Jan 2025\\
Ontario Tech University, Oshawa, ON

\textbf{Bachelor of Technology, Computer Science} \hfill May 2018 -- Jun 2022\\
Punjabi University, Patiala, Punjab, India

\section*{Certifications}

\begin{itemize}[leftmargin=*]
\item Microsoft Certified: Azure Fundamentals AZ-900
\item Microsoft Certified: Azure Administrator Associate AZ-104
\item Palo Alto Networks Certified Network Security Administrator PCNSA
\item Fortinet NSE 1, NSE 2, NSE 3
\item Currently Pursuing CISSP / Security+
\end{itemize}

\section*{Awards \& Leadership}

\begin{itemize}[leftmargin=*]
\item Rising Star Award, KPMG 2023 -- recognized for contributions to security operations and team collaboration.

\item Delivered cybersecurity awareness sessions on cloud security, penetration testing, compliance frameworks, and network security fundamentals.
\end{itemize}

\end{document}